\cvsection{Projects}

\begin{cventries}

 \cventry
    {Semester Project}
    {Android Safety Device}
    {Prof. Sandeep Kumar Yadav}
    {Current Project}
    {
      \begin{cvitems}
    \item {Aim to implement a safety app that tracks the live movement of the user\'s \& displays them to the concerned person. 
    }
    \item {Aim to create a buddy system where a person is able to add friends whose location will be tracked dynamically.
    }
    \item {In case of an emergency, the relatives of that person will be sent an alert verified by the person\'s Image or Voice.}
      \end{cvitems}
    }
    
    \cventry
    {Semester Project}
    {Natural Language Processing}
    {Prof. K.R. Chowdhary}
    {Nov. 2015}
    {
      \begin{cvitems}
    \item {Implemented a search engine able to process query(tokenization). Implemented and scripted in Python.
    }
    \item {Created a dummy database of several weblinks which were searched for the relevant words from the input query using KMP.
    }
    \item {Normalized the search results and displayed the web pages based on their relevance.
    }
      \end{cvitems}
    }
  
  \cventry
    {Course project, Artificial Intelligence}
    {Artificial Intelligence in Game Playing}
    {Prof. K.R. Chowdhary}
    {Sept. 2015}
    {
      \begin{cvitems}
    \item {Implemented Game-Tree search and Monte-Carlo tree search to develop the AI version of 0-sum advanced Tic-Tac-Toe.
    }
    \item {Used Python(Pygame) for UI implementation and human side and C for generating AI moves.
    }
      \end{cvitems}
    }
  
    \cventry
    {Lab Project, Operating Systems and Design}
    {Operating Systems' concepts implementation}
    {Prof. Gaurav Harit}
    {Feb. 2015}
    {
      \begin{cvitems}
    \item {Compared singlethreading and multithreadig computational speed using pthread library of C++ in multiplication of matrices.
    }
    \item {Semaphore implementation, file system implementation using superblock object, file table, file descriptor and basic Linux Shell implementations capable to handle basic I/O operations, piping, append and background processes}
      \end{cvitems}
    }
  
  
 % \cventry
 %   {Participated in Intel Modern Code Developer's challenge 2015}
 %   {Brain Simulation Code(C++)}
 %   {Intel Modern Code Challenge}
 %   {Aug.2015 - Dec. 2015}
 %   {
 %     \begin{cvitems}
 %   \item {Participated in Intel Modern Code Developer Challenge 2015 working on a problem statement of using modern programming techniques such as ‘multithreading’, ‘Cx3D’ etc. to improve the performance of Brain Simulation Code.
  %  }
 %   \item {The code has been developed by researchers at Newcastle University in UK and currently being worked on
  %  through a CERN openlab project.
  %  }
  %  \item {The code is used to simulate the growth of cells in the cerebral cortex often referred %to as ‘grey matter’.
  %  }
  %    \end{cvitems}
  %  }
  
 
\end{cventries}


















%\begin{cvhonors}
% \cvhonor
 % {DEFCON 2016}
  %{Attended lecture and workshops in DEFCON Conference Lucknow}
% {}
%{2016}
% \cvhonor
%  {Ranked under 500}
% {Google APAC Test(Rounds A and B)}
%    {}
%  {2015}
%\cvhonor
%  {Ranked in top 5\%}
% {National Standard Exam in Physics conducted by IAPT and HBCSE}
%{}
%   {2011}
%\cvhonor
% {All India Rank 30}
%{National Junior Talent Search Examination conducted by Govt. of New Delhi}
%    {}
%   {2010}
%\end{cvhonors}

